%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Experience}
\begin{cventries}
	\cventry
	{Staff Software Engineer}
	{Bird}
	{(remote)}
	{February 2016 – Present}
	{\begin{cvitems}
		\item {Enabled the team to implement a scalable web application to support increase in application load by establishing practices and processes for the team to follow.}
		\item {Organized and led a team to update display of data, prioritizing ease-of-us in a widget style interface allowing each component to be exportable.}
		\item {Integrate automatic code style checks into the existing CI/CD system for an application to help other developers learn the front-end ecosystem and paradigms, in order to improve overall code quality and developer experience.}
		\item {Redesigned an existing app increasing performance and reliability by reducing response time for requests from average of 1s to 100ms, with an uptime of 99.99\%.}
		\item {Updated current infrastructure from on-demand instances to auto-scaling groups, allowing for easier deployments and better reliability.}
		\item {Reduced the time to deploy from 18 minutes to 8 minutes by updating the deployment pipeline to support parallel builds and concurrent deployment of applications.}
		\end{cvitems}}
	\cventry
	{Guardium Support Engineer}
	{IBM}
	{Lenexa, KS}
	{April 2015 – February 2016}
	{\begin{cvitems}
		\item {Resolved critical issues in a timely manner prioritizing efficiency and responsiveness by interacting with the development team to discover the root cause of the issues and updating documentation to prevent similar issues from occurring.}
		\item {Resolved tickets that caused outages for enterprise companies within 4 hours, while maintaining a 98\% resolution rate.}
		\item {Reviewed Guardium application logs and Linux system logs to find root causes of issues within the Guardium application and services.}
		\end{cvitems}}
	\cventry
	{Part Time Software Developer}
	{AllofE Solutions}
	{Lawrence, KS}
	{May 2014 – April 2015}
	{\begin{cvitems}
		\item {Designed front end user interface utilizing javascript and PHP, interfacing with a MySQL database.}
		\item {Developed Android application by designing and implementing user interfaces to send and receive data from the database.}
		\item {Updated legacy application written in PHP by introducing metrics to gauge the customer’s needs and fix the issue in a timely manner, leading to a customer satisfaction rate of 99\%.}
		\end{cvitems}}
\end{cventries}

% spacing to keep resume condensed
\vspace{-3mm}
